Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-11 tex/VHzQ.tex
tester_mnras.bib and things_still_todo update

\begin{figure}
    \centering
    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
  \vspace{-14pt}
    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
      (grey colour-scale). }
    \label{fig:W1W2W3}
\end{figure}
\subsection{MIR Colours}
The VH$z$Q with the bluest colour in (W1 - W2) is 
DELS J1048-0109 with (W1-W2) = 0.154. 
%(see Figure~\ref{fig:DELS_J1048}).

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
    \caption{Four of the brightest MIR VH$z$Qs. 
      The thumbnails are the RGB colour outputs using the ALLWISE W1W2W3 bands from the 
      IRSA WISE Image Service, with a scale of 120'' on the side. 
      {\it (a)} UHS J0439+1634 was discovered by
      \citet{Fan2019} and is a strongly lensed quasar at $z=$6.51. 
      {\it (b)} SDSS J0100+2802 is the \citet{Wu2015} object. 
      {\it (c)} SDSS J1443+3623 has {\tt w3mpro, w4mpro } = ($11.189\pm0.1$, $8.699\pm0.26$) and 
      {\it (d)} SDSS J1623+4705 has {\tt w3mpro, w4mpro } = ($11.425\pm0.1$, $8.954\pm0.28$).}
    \label{fig:VHzQ_W4s}
\end{figure*}
The set of VH$z$Q detected in WISE W3 and W4 contains 51 objects that are
detected in the broad W3 filter and 10 objects that are formally detected
in W4 ({\tt w4snr}$\geq$3.0). Four of the brightest W4 objects are
presented in \label{fig:VHzQ_W4s}. UHS J0439+1634
(Fig.~\ref{fig:VHzQ_W4s} (a)) with W4=7.165$\pm$0.12 was discovered by
\citet{Fan2019} and is a strongly lensed quasar at $z=$6.51. This high
luminosity is mostly not intrinsic, but is boosted by an intervening
redshift $z\sim$0.7 galaxy. SDSS J0100+2802 (redshift $z=6.33$) does
not have a formal W4 detection (W4 $=8.98\pm0.45$ and {\tt w4snr}=2.4),
but as reported by \citet{Wu2015}, has a bright detection in the
2MASS $J$, $H$ and $K_{\rm s}$ bands and we report it here.
%%
Other high-redshift quasars that are bright W3/4 objects may well 
also so be lensed, but high-resolution follow-up is needed to confirm.

@@

Quasars are known to have dramatically changing Balmer lines, especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016, Gezari2017, Runco2016, Yang2017, Assef2018, Stern2018, Wang2018, Ross2018, MacLeod2019, Graham2019}. As a guide, we note that H$\alpha$ is redshifted to 3.94$\mu$ (i.e. W1) at $z=5.00$ and 5.57$\mu$m, which is between the W2 and W3-bands at $z=7.50$. 
H$\beta$ is redshifted to 2.92$\mu$m, which is the blue edge of W1, at $z=5.00$ and 
4.13$\mu$m at $z=7.50$. 
%%
Less well understood is the temporal behvaiour of the metal lines, in particular \civ and \mgii. 
\civ enters the
$Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the
$J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the
$H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the
$K$-band at redshift $z=6.25$ and exits at $7.50$.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
  \vspace{-14pt}
    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
      (grey colour-scale). }
    \label{fig:W1W2W3}
\end{figure}
\subsection{MIR Colours}
%
\citet{LaMassa2017, Glikman2018, LaMassa2019} 
%

The VH$z$Q with the bluest colour in (W1 - W2) is 
DELS J1048-0109 with (W1-W2) = 0.154. 
%(see Figure~\ref{fig:DELS_J1048}).

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
    \caption{Four of the brightest MIR VH$z$Qs. 
      The thumbnails are the RGB colour outputs using the ALLWISE W1W2W3 bands from the 
      IRSA WISE Image Service, with a scale of 120'' on the side. 
      {\it (a)} UHS J0439+1634 was discovered by
      \citet{Fan2019} and is a strongly lensed quasar at $z=$6.51. 
      {\it (b)} SDSS J0100+2802 is the \citet{Wu2015} object. 
      {\it (c)} SDSS J1443+3623 has {\tt w3mpro, w4mpro } = ($11.189\pm0.1$, $8.699\pm0.26$) and 
      {\it (d)} SDSS J1623+4705 has {\tt w3mpro, w4mpro } = ($11.425\pm0.1$, $8.954\pm0.28$).}
    \label{fig:VHzQ_W4s}
\end{figure*}
The set of VH$z$Q detected in WISE W3 and W4 contains 51 objects that are
detected in the broad W3 filter and 10 objects that are formally detected
in W4 ({\tt w4snr}$\geq$3.0). Four of the brightest W4 objects are
presented in \label{fig:VHzQ_W4s}. UHS J0439+1634
(Fig.~\ref{fig:VHzQ_W4s} (a)) with W4=7.165$\pm$0.12 was discovered by
\citet{Fan2019} and is a strongly lensed quasar at $z=$6.51. This high
luminosity is mostly not intrinsic, but is boosted by an intervening
redshift $z\sim$0.7 galaxy. SDSS J0100+2802 (redshift $z=6.33$) does
not have a formal W4 detection (W4 $=8.98\pm0.45$ and {\tt w4snr}=2.4),
but as reported by \citet{Wu2015}, has a bright detection in the
2MASS $J$, $H$ and $K_{\rm s}$ bands and we report it here.
%%
Other high-redshift quasars that are bright W3/4 objects may well 
also so be lensed \citep[e.g.,][]{Glikman2018lens, Fan2019}, 
but high-resolution follow-up is needed to confirm.

@@

Quasars are known to have dramatically changing Balmer lines, especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016, Gezari2017, Runco2016, YangQ2018, Assef2018, Stern2018, Ross2018, MacLeod2019, Graham2019}. As a guide, we note that H$\alpha$ is redshifted to 3.94$\mu$ (i.e. W1) at $z=5.00$ and 5.57$\mu$m, which is between the W2 and W3-bands at $z=7.50$. 
H$\beta$ is redshifted to 2.92$\mu$m, which is the blue edge of W1, at $z=5.00$ and 
4.13$\mu$m at $z=7.50$. 
%%
Less well understood is the temporal behvaiour of the metal lines, in particular \civ and \mgii. 
\civ enters the
$Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the
$J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the
$H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the
$K$-band at redshift $z=6.25$ and exits at $7.50$.
